Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility

### 2025-11-17 paper/07-supplementary-material.qmd
Big up methods and results

This section presents the supplementary material for this study. First, graphs are shown for the evaluation of the balance of IPW-ATT via entropy balance. Second, the complete estimated regression models are shown. Finally, the sensitivity analyses performed are shown.

@@

@@

@@

```{r}
#| label: tbl-holm
#| tbl-cap: "Holm correction"
#| tbl-cap-location: top
#| results: asis
#| echo: false

data.frame(traj = c("Low→Middle","Low→High","Middle→Low","Middle→High","High→Middle","High→Low"),
           p_raw = p, p_holm = p_holm) %>% 
  mutate_at(.vars = c(2,3), .funs = ~ round(.,3)) %>% 
  mutate_at(.vars = c(2,3), .funs = ~ format(., nsmall=3)) %>% 
  mutate_all(~ as.character(.)) %>% 
  kableExtra::kable(format = table_format, 
                    col.names = c("Mobility treatment", "p value", "Holm"),
                    row.names = F,
                    booktabs = T, align = 'l',
                    caption = NULL) %>% 
  kableExtra::kable_styling(latex_options = "hold_position", 
                            position = "center") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>% 
  kableExtra::row_spec(0, bold = T) %>% 
  kableExtra::add_footnote(label = c("Note: p values derived from Table 1"), notation = "none")

```{r}
#| label: tbl-evalues
#| tbl-cap: "E-values for ATT estimates by mobility trajectory (Ding & VanderWeele, 2016 approximation)"
#| tbl-cap-location: top
#| results: asis
#| echo: false

evalues_tbl %>% 
  mutate_at(.vars = c(2:12), .funs = ~ round(.,3)) %>% 
  mutate_at(.vars = c(2:11), .funs = ~ format(., nsmall=3)) %>% 
  mutate_all(~ as.character(.)) %>% 
  tidyr::unite("ci", ci_low:ci_high, sep = ";") %>% 
  kableExtra::kable(format = table_format, 
                    col.names = c("Mobility treatment", "Beta", "CI 95% [low-upper]", "sdY", "RR point", "RR point upper", "E point", "RR CI", "RR CI Upper", "E CI", "CI Crosses 0"),
                    row.names = F,
                    booktabs = T, 
                    align = 'l',
                    caption = NULL) %>% 
  kableExtra::kable_styling(latex_options = "hold_position", 
                            position = "center") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = T, font_size = 8) %>% 
  kableExtra::row_spec(0, bold = T)
```

>>>>

This section presents the supplementary material for this study.

@@

## Descriptive statistics

```{r}
#| label: tbl-summary1
#| tbl-cap: "Descriptive statistics for all variables."
#| tbl-cap-location: top
#| results: asis
#| echo: false

library(summarytools)
t1 <- db %>% 
  select(just_pension_f, 
         estrato_orig, 
         estrato_ocupa, 
         educ_orig_f,
         hogar_bip_f, 
         nacionalidad_f, 
         sexo_f,
         m0_edad_f, 
         etnia_f, 
         merit_i,
         wave

t1 <- t1 %>% 
  mutate(
    just_pension_f = factor(just_pension_f, levels = c(0,1), labels = c("Disagree", "Agree")),
    hogar_bip_f  = factor(hogar_bip_f, levels = c(0,1), labels = c("No co-residence", "Co-residence")),
    #nacionalidad_f = if_else(nacionalidad_f == 0, 1, 0),
    nacionalidad_f  = factor(nacionalidad_f, levels = c(0,1), labels = c("Non-Chilean", "Chilean")),
    #sexo_f = if_else(sexo_f == 1, 0, 1),
    sexo_f  = factor(sexo_f, levels = c(0,1), labels = c("Male", "Female")),
    etnia_f = factor(etnia_f, levels = c(0,1), labels = c("Non-indigenous", "Indigenous"))
  )

t1$just_pension_f <- sjlabelled::set_label(t1$just_pension_f, "Preference for pension commodification")
t1$educ_orig_f <- sjlabelled::set_label(t1$educ_orig_f, "Parental education")
t1$hogar_bip_f <- sjlabelled::set_label(t1$hogar_bip_f, "Co-residence with both parents at age 15")
t1$nacionalidad_f <- sjlabelled::set_label(t1$nacionalidad_f, "Nacionality")
t1$sexo_f <- sjlabelled::set_label(t1$sexo_f, "Sex")
t1$m0_edad_f <- sjlabelled::set_label(t1$m0_edad_f, "Age (in years)")
t1$etnia_f <- sjlabelled::set_label(t1$etnia_f, "Indigenous ethnicity")
t1$merit_i <- sjlabelled::set_label(t1$merit_i, "Meritocracy perception")
t1$wave <- sjlabelled::set_label(t1$wave, "Wave")

df<-dfSummary(t1,
               plain.ascii = FALSE,
               style = "multiline",
               tmp.img.dir = "/tmp",
               graph.magnif = 0.75,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = F, # plot
               valid.col = T, # n valido
               col.widths = c(30,10,10,10))

df$Variable <- NULL # delete variable column

print(df)

## Balance evaluation

@@

## Mobility effects models

@@

{{< pagebreak >}}

## Robustness check and sensitivity analysis

```{r}
#| label: tbl-robus1
#| tbl-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification coded as 3-5 vs. 1-2, with covariates and wave fixed effects."
#| tbl-cap-location: top
#| results: asis
#| echo: false

texreg::texreg(list(mp_lm_r_i,
                       mp_lh_r_i,
                       mp_mh_r_i,
                       mp_ml_r_i,
                       mp_hm_r_i,
                       mp_hl_r_i),
                  custom.model.names = c(
                    "Low-Middle",
                    "Low-High",
                    "Middle-High",
                    "Middle-Low",
                    "High-Middle",
                    "High-Low"
                  ),   caption.above = NULL,
               caption = NULL,
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 9:10),
               custom.note = "Note: Cells contain regression coefficients with confidence intervals in parentheses. %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.7,
               center = T,
               float.pos = "H!")
```

```{r}
#| label: tbl-robus2
#| tbl-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification excluding intermediate category, with covariates and wave fixed effects."
#| tbl-cap-location: top
#| results: asis
#| echo: false

texreg::texreg(list(mp_lm_r_ii,
                       mp_lh_r_ii,
                       mp_mh_r_ii,
                       mp_ml_r_ii,
                       mp_hm_r_ii,
                       mp_hl_r_ii),
                  custom.model.names = c(
                    "Low-Middle",
                    "Low-High",
                    "Middle-High",
                    "Middle-Low",
                    "High-Middle",
                    "High-Low"
                  ),   caption.above = NULL,
               caption = NULL,
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 9:10),
               custom.note = "Note: Cells contain regression coefficients with confidence intervals in parentheses. %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.7,
               center = T,
               float.pos = "H!")
```

```{r}
#| label: tbl-robus3
#| tbl-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification using the original 5-point likert scale, with covariates and wave fixed effects."
#| tbl-cap-location: top
#| results: asis
#| echo: false

texreg::texreg(list(mp_lm_r_iii,
                       mp_lh_r_iii,
                       mp_mh_r_iii,
                       mp_ml_r_iii,
                       mp_hm_r_iii,
                       mp_hl_r_iii),
                  custom.model.names = c(
                    "Low-Middle",
                    "Low-High",
                    "Middle-High",
                    "Middle-Low",
                    "High-Middle",
                    "High-Low"
                  ),   caption.above = NULL,
               caption = NULL,
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 9:10),
               custom.note = "Note: Cells contain regression coefficients with confidence intervals in parentheses. %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.7,
               center = T,
               float.pos = "H!")
```

```{r}
#| label: tbl-evalues1
#| tbl-cap: "E-values for ATT estimates for Middle-High trajectory (Cinelli & Hazlett, 2020 approximation)"
#| tbl-cap-location: top
#| results: asis
#| echo: false

ovb_minimal_reporting(mh_evalue, format = "latex")
```

```{r}
#| label: tbl-evalues2
#| tbl-cap: "E-values for ATT estimates for High-Middle trajectory (Cinelli & Hazlett, 2020 approximation)"
#| tbl-cap-location: top
#| results: asis
#| echo: false

ovb_minimal_reporting(hm_evalue, format = "latex")
```

```{r}
#| label: tbl-evalues3
#| tbl-cap: "E-values for ATT estimates for High-Low trajectory (Cinelli & Hazlett, 2020 approximation)"
#| tbl-cap-location: top
#| results: asis
#| echo: false

ovb_minimal_reporting(hl_evalue, format = "latex")
```

### 2025-11-17 paper/paper.qmd
Update entrega 1
Up SP
Big up methods and results

---
title: "Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
    code-link: true
    title-block-banner: true
    theme:
      - pretty.scss
  pdf: 
    pdf-engine: xelatex
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/tesis-magister.bib"
csl: "../input/bib/apa6.csl"
author:
  - name: Andreas Laffert Tamayo
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 1
affiliations: 
  - id: 1
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
citeproc: true
abstract: | 
 My abstract
  \newline
 **Keywords**: pension commodification, social mobility, causal inference, Chile, public preferences
link-citations: true
linestretch: 1.5
mainfont: Times New Roman
fontsize: 13pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

@@

>>>>

---
title: "Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
    code-link: true
    title-block-banner: true
    theme:
      - pretty.scss
  pdf: 
    pdf-engine: xelatex
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/tesis-magister.bib"
csl: "../input/bib/apa6.csl"
author:
  - name: Andreas Laffert Tamayo
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 1
affiliations: 
  - id: 1
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
citeproc: true
abstract: | 
 My abstract
  \newline
 **Keywords**: Pension commodification · Intergenerational mobility · Causal inference · Meritocracy · Chile
link-citations: true
linestretch: 1.5
mainfont: Times New Roman
fontsize: 13pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

@@

::: {pagebreak}
:::
